\item \textbf{Enterprise Governance:} Acted as the primary security representative on Vermeer's IT Architecture Committee, directly influencing multi-million dollar technology decisions and driving the adoption of enterprise-wide architectural standards.
\item \textbf{DevSecOps Program Establishment:} Directed the architectural roadmap and strategic governance for the Enterprise Application Security Program across all product lines (SaaS, vehicles, B2B applications). Implemented Secure-by-Design pipelines for 15+ development teams, reducing security debt for critical applications.
\item \textbf{Product Security Validation:} Created a product security validation framework consisting of threat modeling, continuous automated security reviews, and offensive security engagements on proprietary machine operating platforms and associated cloud APIs to validate security efficacy prior to market deployment.
\item \textbf{OT ZTNA Architecture:} Architected and directed the implementation of a Zero Trust Network Access (ZTNA) overlay for autonomous industrial vehicles. This project enforced micro-segmentation, mitigating cyber-physical risks and reducing the potential attack surface exposure.
\item \textbf{Policy as Code:} Established enterprise Policy as Code standards and automated governance using custom orchestration tooling (GitHub API integration). Automated enforcement checks and remediations across 1500+ repositories, eliminating manual compliance audits.
\item \textbf{Advanced Detection Engineering:} Designed, implemented, and operationalized a proactive threat detection system (custom honeypots, analysis tools, detection lab). Developed hundreds of high-fidelity Kusto Query Language (KQL) rules, improving threat detection accuracy.
\item \textbf{Incident Response Leadership:} Directed and executed high-stakes incident response (IR) investigations across complex, multi-domain environments (IT, Cloud, OT), successfully containing and eradicating ransomware affiliates and supply chain attacks.